README

### 2017-04-11 src/README.Rmd
Update journal list and add csv of comments/DOI
Update journal list to use "Virology Journal (Plant Viruses Section)"

Add "data/journals.csv", which contains the randomised journal
information with DOIs and comments about the journals to be merged with
bibliography once both are completed.

Update packages via packrat

```{r journal_list}
journal_list <- tibble(
  seq(1:21),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Journal of Plant Virology",
    "Molecular Plant-Microbe Interactions",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

>>>>

```{r journal_list}
journal_list <- tibble(
  seq(1:21),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Virology Journal (Plant Viruses Section)",
    "Molecular Plant-Microbe Interactions",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))
